Analyzing Trends in U.S. Residential Real Estate Prices

### 2024-04-17 outputs/paper/paper.qmd
paper updated

---
title: "Analyzing Trends in U.S. Residential Real Estate Prices"
subtitle: "A Data-Driven Approach to Understand the Market"
author: 
  - Ziheng Zhong
thanks: "Code and data are available at: https://github.com/iJustinn/House_Price.git"
date: today
date-format: long
abstract: "This research examines the dynamics of the U.S. housing market, offering a detailed analysis of price trends across various states and types of housing, which have shown considerable increases in recent years. The study clarifies how factors such as location, property characteristics, and external economic influences impact house prices."
format: pdf
toc: true
toc-depth: 3
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Analyzing Trends in U.S. Residential Real Estate Prices"
subtitle: "A Data-Driven Approach to Understand the Market"
author: 
  - Ziheng Zhong
thanks: "Code and data are available at: https://github.com/iJustinn/House_Price.git"
date: today
date-format: long
abstract: "This research conducts a detailed analysis of U.S. residential real estate price trends over the past two decades, using data from Zillow to explore influences from geographic location, property characteristics, and economic indicators. By employing multiple regression models, polynomial regression, and Generalized Additive Models (GAM), the study identifies complex interactions that affect housing prices. It highlights a notable shift towards larger homes, potentially driven by changes in work and lifestyle patterns due to recent global events."
format: pdf
toc: true
toc-depth: 3
number-sections: true
bibliography: references.bib
---
